Hijacking Simulators for the Greater Good

### 2019-04-26 paper/icml_ai4good/main.tex
updated

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2019}
\newcommand{\bg}[1]{~{{[{\it \textcolor{red}{{\bf BG:} #1}}]}}}
\newcommand{\cs}[1]{~{{[{\it \textcolor{red}{{\bf CS:} #1}}]}}}
\newcommand{\ag}[1]{~{{[{\it \textcolor{red}{{\bf AG:} #1}}]}}}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2019}
\usetikzlibrary{arrows,chains,matrix,positioning,scopes}
%
\makeatletter
\tikzset{join/.code=\tikzset{after node path={%
\ifx\tikzchainprevious\pgfutil@empty\else(\tikzchainprevious)%
edge[every join]#1(\tikzchaincurrent)\fi}}}
\makeatother
%
\tikzset{>=stealth',every on chain/.append style={join},
         every join/.style={->}}
\tikzstyle{labeled}=[execute at begin node=$\scriptstyle,
   execute at end node=$]
% The \icmltitle you define below is probably too long as aer.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Understanding the Black-box Structure of Epidemiology Simulators for Policy Decision Making}

@@

\twocolumn[
\icmltitle{Understanding the Black-box Structure of Epidemiology Simulators\\
			 for Policy Decision Making}

@@

A goal of probabilistic programming is to couple simulators, with inference. This is 
because stochastic simulators are used prominently in many industrial settings,
do not require one to construct hand-crafted joint distributions as they implicitly 
define a joint distribution of the program and encode learnt structures 
directly. This makes simulators powerful tools and much of machine learning (ML) and 
Artificial Intelligence (AI)
can be seen as trying to emulate such simulators from a purely data-driven approach.
However, in the 
ML/AI setting, although we can often infer outcomes, we have little understanding about what 
in the data led to the outputted inferences. 
This makes it challenging to deploy ML/AI systems into the wild, especially in health-related and safety-critical domains, such
as epidemiology, as we lose \emph{interpretability}. 
In this work, we explain how to design ML/AI systems that combine
probabilistic programming systems (PPSs) and epidemiology simulators, to extract
fully interpretable structures, enabling policy makers 
and practitioners to make decisions from simulator outputs that can be fully resoned on.
 % interpretable inferences. 
In particular, we demonstrate this for the Malaria disease in two commonly used simulators; EMOD and OpenMalaria.
\end{abstract}

@@

\subsection{Extending Probabilistic Programming Protocols}
\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,-0.15)},
      anchor=north,legend columns=-1},
      xlabel = {Address},
    ylabel={Probabilities},
    symbolic x coords={Trace 1, Trace 2, Trace 3},
    xtick=data,
    nodes near coords,
    nodes near coords align={vertical},
    ]
% \addplot coordinates {(tool8,7) (tool9,9) (tool10,4)};
\addplot coordinates {(Trace 1,0.2) (Trace 2,0.5) (Trace 3,0.23)};
% \addplot coordinates {(A1,0.2) (A2,0.5) (A3,0.7) (A4,0.9)};
% \addplot coordinates {(A1,0.1) (A2,0.1) (A3,0.1) (A4,0.3)};
% \legend{used,understood,not understood}
\end{axis}
\end{tikzpicture}
\caption{Trace probabilities. Trace 1 corresponds to A1,A1,A4,... 
Trace 2 corresponds to A1,A1,A1,...A2,... These still need correctly calculating.}
\end{figure}
\begin{figure*}[h!]
	\centering
	\includegraphics[width=\textwidth]{../plots/ewan_25_pop_10.pdf}
	\centering
	\includegraphics[width=\textwidth]{../plots/ewan_25_pop_100.pdf}
	\caption{Add something. Population 100}
	\label{fig:plotewan}
\end{figure*}

>>>>

% \usepgfplotslibrary{external}
% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2019}
\newcommand{\bg}[1]{~{{[{\it \textcolor{red}{{\bf BG:} #1}}]}}}
\newcommand{\cs}[1]{~{{[{\it \textcolor{red}{{\bf CS:} #1}}]}}}
\newcommand{\ag}[1]{~{{[{\it \textcolor{red}{{\bf AG:} #1}}]}}}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2019}
\usetikzlibrary{arrows,chains,matrix,positioning,scopes}
%
\makeatletter
\tikzset{join/.code=\tikzset{after node path={%
\ifx\tikzchainprevious\pgfutil@empty\else(\tikzchainprevious)%
edge[every join]#1(\tikzchaincurrent)\fi}}}
\makeatother
%
\tikzset{>=stealth',every on chain/.append style={join},
         every join/.style={->}}
\tikzstyle{labeled}=[execute at begin node=$\scriptstyle,
   execute at end node=$]
% The \icmltitle you define below is probably too long as aer.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Hijacking Simulators for the Greater Good}

@@

\twocolumn[
\icmltitle{Hijacking Simulators for the Greater Good}

@@

A goal of probabilistic programming is to couple simulators, with inference. This is 
because stochastic simulators are used prominently in many industrial settings,
do not require one to construct hand-crafted joint distributions as they implicitly 
define a joint distribution of the program and encode learnt structures 
directly. This makes simulators powerful tools and much of machine learning (ML) and 
Artificial Intelligence (AI)
can be seen as trying to emulate such simulators from a purely data-driven approach.
However, in the 
ML/AI setting, although we can often infer outcomes, we have little understanding about what 
in the data led to the outputted inferences. 
This makes it challenging to deploy ML/AI systems into the wild, especially in health-related and safety-critical domains, such
as epidemiology, as we lose \emph{interpretability}. 
In this work, we explain how to design ML/AI systems that combine
probabilistic programming systems (PPSs) and epidemiology simulators, to extract
fully interpretable structures, enabling policy makers 
and practitioners to make decisions from simulator outputs that can be fully reasoned on.
 % interpretable inferences. 
In particular, we demonstrate this for the Malaria disease in two commonly used simulators; EMOD and OpenMalaria.
\end{abstract}

@@

\subsection{Extending Probabilistic Programming Protocols}

\bg{Add performance plot showing memory consumptions of pyprob and our new system.}
% \begin{tikzpicture}
% \begin{axis}[xlabel={Population size},ylabel={memory consumption (MB)},
% legend style={at={(0.5,-0.15)},xmin=0,xmax=700,ymin=0,ymax=70, axis lines=center]

% \addplot[pyprob,domain=0:1000, color=blue,]{x};

% \addplot[improved,domain=0:1000, color=red,]{10};

% \legend{pyprob, improved}
% \end{axis}
% \end{tikzpicture}

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,-0.15)},
      anchor=north,legend columns=-1},
      xlabel = {Address},
    ylabel={Probabilities},
    symbolic x coords={Trace 1, Trace 2, Trace 3},
    xtick=data,
    nodes near coords,
    nodes near coords align={vertical},
    ]
% \addplot coordinates {(tool8,7) (tool9,9) (tool10,4)};
\addplot coordinates {(Trace 1,0.2) (Trace 2,0.5) (Trace 3,0.23)};
% \addplot coordinates {(A1,0.2) (A2,0.5) (A3,0.7) (A4,0.9)};
% \addplot coordinates {(A1,0.1) (A2,0.1) (A3,0.1) (A4,0.3)};
% \legend{used,understood,not understood}
\end{axis}
\end{tikzpicture}
\caption{Trace probabilities. Trace 1 corresponds to A1,A1,A4,... 
Trace 2 corresponds to A1,A1,A1,...A2,... These still need correctly calculating.}
\end{figure}
\begin{figure*}[h!]
	\centering
	\includegraphics[width=\textwidth]{../plots/ewan_25_pop_10.pdf}
	\centering
	\includegraphics[width=\textwidth]{../plots/ewan_25_pop_100.pdf}
	\caption{Add something. Population 100}
	\label{fig:plotewan}
\end{figure*}
